Ms 1

### 2017-10-07 ms1/ms1_display.Rmd
cleanups

est2pct = function(x) (exp(x) - 1)*100
mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*std.error)
}
model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f (%.2f -- %.2f)', pct_change, ci_low, ci_high))
}

@@

pde_approp_risk_2011 = pde_approp_table %>%
  # add up tiers 1 and 2
  filter(year==2011, tier <= 2) %>%
  group_by(antibiotic) %>%
  summarize(risk_2011=sum(f))

@@

# compute risk ratios
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_approp_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p)
  # now estimate is adjusted change in INappropriate prescribing

@@

```{r hcpcs_count}
read_tsv('tables/hcpcs_count.tsv') %>%
  group_by(hcpcs_flag) %>%
  summarize(n_dx=sum(n_dx)) %>%
  mutate(f=n_dx/sum(n_dx)) %>%
  kable
```

@@

```{r pde_with_dx_upstream}
read_tsv('tables/pde_with_dx_upstream.tsv') %>%
  group_by(has_dx, has_em_dx) %>%
  summarize(n=sum(n)) %>%
  ungroup() %>%
  mutate(f=n/sum(n), cumf=cumsum(f)) %>%
  kable
```

@@

@@

```{r pde_approp_trends}
read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  select(antibiotic, estimate, p.value) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('overall', top_abx))) %>%
  arrange(antibiotic) %>%
  kable
```

>>>>

est2pct = function(x) (exp(x) - 1)*100

mult_est = function(df, m) {
  mutate(df, estimate=m*estimate, std.error=sqrt(m)*std.error)
}

model_ci = function(df) {
  df %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f (%.2f -- %.2f)', pct_change, ci_low, ci_high))
}

@@

pde_inapprop_risk_2011 = pde_approp_table %>%
  # add up tiers 3 and 4
  filter(year==2011, tier > 2) %>%
  group_by(antibiotic) %>%
  summarize(risk_2011=sum(f))

@@

# compute risk ratios
pde_inapprop_trends = read_tsv('tables/pde_inapprop_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_inapprop_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p)
  # now estimate is adjusted change in INappropriate prescribing

@@

```{r hcpcs_count}
hcpcs_count = read_tsv('tables/hcpcs_count.tsv') %>%
  group_by(hcpcs_flag) %>%
  summarize(n_dx=sum(n_dx)) %>%
  mutate(f=n_dx/sum(n_dx))

hcpcs_count %>% kable
```

This equals a total of `r prettyNum(sum(hcpcs_count$n_dx), big.mark=',')` diagnoses.

@@

```{r pde_with_dx_upstream}
read_tsv('tables/pde_with_dx_upstream.tsv') %>%
  group_by(has_dx, has_em_dx) %>%
  summarize(n=sum(n)) %>%
  ungroup() %>%
  mutate(f=n/sum(n), cumf=cumsum(f), cumf1=1-cumf) %>%
  kable
```

@@

```{r pde_approp_table}
pde_approp_table %>%
  mutate(approp=tier <= 2) %>%
  group_by(approp) %>%
  summarize(n=sum(n)) %>%
  mutate(f=n/sum(n)) %>%
  kable
```

@@

```{r pde_approp_trends}
read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  #select(antibiotic, estimate, p.value) %>%
  mult_est(3) %>%
  model_ci() %>%
  mutate(antibiotic=factor(antibiotic, levels=c('overall', top_abx))) %>%
  arrange(antibiotic) %>%
  select(antibiotic, pct_change, ci_low, ci_high, p.value) %>%
  kable
```
